Milk intake and risk of mortality risk in the Japan Collaborative Cohort Study - a Bayesian survival analysis

### 2020-06-22 Paperfolder/Paperfolder.Rmd
updated expo and endpoint

Frequency of milk intake during the preceding year of the baseline was assessed by FFQ from "never", "1-2 times/month", "1-2 times/week", "3-4 times/week", and "Almost daily".

>>>>

Frequency of milk intake during the preceding year of the baseline was assessed by FFQ from "never", "1-2 times/month", "1-2 times/week", "3-4 times/week", and "Almost daily". The exact amount of milk consumption was difficult to assess here. However, good reproducibility and validity were confirmed previously (Spearman rank correlation coefficient between milk intake frequency and weighed dietary record for 12 days was 0.65) [@Date2005].

The causes and date of death were obtained from death certificates and were systematically reviewed. The follow-up period was defined as from the time of the baseline survey was completed, which was between 1988-1990, until the end of 2009 (administrative censor), or the date when move-out of study area, or the date of death from stroke recorded, whichever occurred first. Other causes of death were treated as censored and assumed not informative. The causes of death were coded by the 10th Revision of the International Statistical Classification of Diseases and Related Health Problems (ICD-10), therefore stroke was defined as I60-I69. We further classified these deaths into hemorrhagic stroke (I60, I61 and I62) or cerebral infarction (I63) when subtypes of stroke in their death certificate were available.

## Statistical approach

### 2020-06-22 Paperfolder/Paperfolder.tex
updated expo and endpoint

Frequency of milk intake during the preceding year of the baseline was
assessed by FFQ from ``never'', ``1-2 times/month'', ``1-2 times/week'',
``3-4 times/week'', and ``Almost daily''.

>>>>

Frequency of milk intake during the preceding year of the baseline was
assessed by FFQ from ``never'', ``1-2 times/month'', ``1-2 times/week'',
``3-4 times/week'', and ``Almost daily''. The exact amount of milk
consumption was difficult to assess here. However, good reproducibility
and validity were confirmed previously (Spearman rank correlation
coefficient between milk intake frequency and weighed dietary record for
12 days was 0.65) \citep{Date2005}.

The causes and date of death were obtained from death certificates and
were systematically reviewed. The follow-up period was defined as from
the time of the baseline survey was completed, which was between
1988-1990, until the end of 2009 (administrative censor), or the date
when move-out of study area, or the date of death from stroke recorded,
whichever occurred first. Other causes of death were treated as censored
and assumed not informative. The causes of death were coded by the 10th
Revision of the International Statistical Classification of Diseases and
Related Health Problems (ICD-10), therefore stroke was defined as
I60-I69. We further classified these deaths into hemorrhagic stroke
(I60, I61 and I62) or cerebral infarction (I63) when subtypes of stroke
in their death certificate were available.

\hypertarget{statistical-approach}{%
\subsection{Statistical approach}\label{statistical-approach}}
